Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-07 paper/paper.tex

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:engines}Engines selected.}
  \begin{tabular}{cccrrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB & Version \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 & xxxx\\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008 & 8.4.138\\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009 & xxxx\\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & 1100+ & Mar 1996 & 76.0b6\\
    Facebook & \hermes & \cite{hermes2020repo} & 5400+ & Jul 2019 & 0.5.0\\
   \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:engines}Engines selected.}
  \begin{tabular}{cccrrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB & Version \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
    \multicolumn{1}{c}{3300+} & Jun 2001\\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
    \multicolumn{1}{c}{1100+} & Mar 1996\\
    Facebook & \hermes{} & \cite{hermes2020repo} &
    \multicolumn{1}{c}{5400+} & Jun 2019\\
   \bottomrule
  \end{tabular}
\end{table}
